|

### 2023-04-03 paper.Rmd
Auto stash before merge of "master" and "origin/master"

```{r}
# OOP supports needed by `visage`
# remotes::install_github("TengMCing/bandicoot")
# 
# Visual inference models and p-value calculation
# remotes::install_github("TengMCing/visage")

@@

```{r sensitivity, fig.cap = "Change of $p$-values with $\\hat{\\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line is to indicate $p\\text{-value} = 0.05$. The x-axis is drawn on logarithmic scale. For multiplier smaller than $1$, the adjusted $p$-value will incrase then decrase as $p$-value increases. The trend is the opposite for multiplier greater than $1$, but the difference will eventually reach $0$."}
upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  mutate(diff_p_value = adjusted_p_value - p_value) %>%
  ggplot() +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0.05, col = "red", linetype = 2) +
  geom_point(aes(p_value, diff_p_value), alpha = 0.2) +
  scale_x_log10() +
  facet_wrap(~modified) +
  ylab(expression("Adjusted"~italic(p)*"-value minus"~italic(p)*"-value")) +
  xlab(expression(italic(p)*"-value")) +
  theme_light()

```

@@

```{r n_eval, fig.cap = "Change of power of visual tests for different number of evalutions on lineups with uniform fitted value distribution. The power will incrase as the number of evaluations increases, but the margin will decrase."}
eval_n <- function(n_eval, boot) {
  map_df(1:boot, function(boot_id) {
  vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  group_by(unique_lineup_id) %>%
  slice_sample(n = n_eval) %>%
  ungroup() %>%
  calc_p_value_multi(lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha) %>%
  mutate(boot_id = boot_id)
}) %>%
  left_join(select(vi_survey, unique_lineup_id, effect_size)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(-unique_lineup_id, -p_value) %>%
  mutate(n_eval = n_eval)
}

>>>>

```{r}
# OOP supports needed by `visage`
# remotes::install_github("TengMCing/bandicoot")
# 
# Visual inference models and p-value calculation
# remotes::install_url("https://github.com/TengMCing/visage/raw/master/built/visage_0.1.0.tar.gz")

@@

```{r sensitivity, fig.cap = "Change of $p$-values with $\\hat{\\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line is to indicate $p\\text{-value} = 0.05$. The x-axis is drawn on logarithmic scale. For multiplier smaller than $1$, the adjusted $p$-value will incrase then decrase as $p$-value increases. The trend is the opposite for multiplier greater than $1$, but the difference will eventually reach $0$."}
upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  mutate(diff_p_value = adjusted_p_value - p_value) %>%
  ggplot() +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0.05, col = "red", linetype = 2) +
  geom_point(aes(p_value, diff_p_value), alpha = 0.2) +
  facet_wrap(~modified) +
  ylab(expression("Adjusted"~italic(p)*"-value minus"~italic(p)*"-value")) +
  xlab(expression(italic(p)*"-value")) +
  theme_light() +
  scale_x_continuous(breaks = c(0.0001, 0.001, 0.01, 0.1, 1),
                     minor_breaks = NULL,
                     trans = "log10",
                     labels = c("0.01%", "0.1%", "1%", "10%", "100%"))
```

@@

```{r n_eval, fig.cap = "Change of power of visual tests for different number of evalutions on lineups with uniform fitted value distribution. The power will incrase as the number of evaluations increases, but the margin will decrase.", fig.height = 4}
eval_n <- function(n_eval, boot) {
  map_df(1:boot, function(boot_id) {
  vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  group_by(unique_lineup_id) %>%
  slice_sample(n = n_eval) %>%
  ungroup() %>%
  calc_p_value_multi(lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha) %>%
  mutate(boot_id = boot_id)
}) %>%
  left_join(select(vi_survey, unique_lineup_id, effect_size)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(-unique_lineup_id, -p_value) %>%
  mutate(n_eval = n_eval)
}
